---
title: "Carbon Pools in R"
author: "Marco Baldo"
date: "2024-04-05"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Theory behind the statistical function

The `quantile` function calculates quantiles based on a specified probability distribution. The formula for calculating the quantiles is based on the definition of quantiles and the probability distribution. 

The formula for the quantile at probability `p` (where `p` is a value between 0 and 1) is defined as:

\[
Q(p) = (1 - g) \times x[j] + g \times x[j+1] \quad \text{(Eq. 1)}
\]

Where:

- \( Q(p) \) is the quantile at probability \( p \).
- \( x[j] \) is the \( j \)-th order statistic, which is the data point just below the \( p \)-th percentile.
- \( x[j+1] \) is the \( j+1 \)-th order statistic, which is the data point just above the \( p \)-th percentile.
- \( g \) is the fractional part of the index \( j \) (i.e., the decimal portion).
  
The `quantile` function in R uses linear interpolation to calculate quantiles. It estimates the quantiles by finding the order statistics \( x[j] \) and \( x[j+1] \) based on the specified \( p \), and then performs the linear interpolation using the formula above to estimate the quantile value.
  
In simpler terms, the `quantile` function finds the two data points that bound the specified quantile, calculates a weighted average of those points, and returns the estimated quantile value. This allows you to divide your data into segments based on the specified probabilities (e.g., quartiles at \( p = 0, 0.333333333333, 0.66666666666, 1 \)).



Table 1. Tables of deadwood decay classes per tree genus or tree functional type aggregated.

| Species   | Decay Class 1 | Decay Class 2 | Decay Class 3 | Decay Class 4 | Decay Class 5 |
|-----------|---------------|---------------|---------------|---------------|---------------|
| Abies     | 343           | 305           | 247           | 174           | 149           |
| Alnus     | 422           | 359           | 286           | 197           | 120           |
| Deciduous | 523           | 442           | 345           | 241           | 152           |
| Carpinus  | 428           | 392           | 336           | 211           | 140           |
| Conifer   | 374           | 334           | 271           | 198           | 160           |
| Fagus     | 520           | 379           | 261           | 229           | 220           |
| Fraxinus  | 452           | 403           | 392           | 227           | 151           |
| Picea     | 381           | 340           | 270           | 190           | 157           |
| Pinus     | 379           | 334           | 277           | 214           | 165           |
| Quercus   | 614           | 518           | 397           | 300           | 195           |

Tables of deadwood decay classes per tree genus or tree functional type aggregated. All the values are expressed as dry biomass per volume \( \text{kg} \cdot \text{m}^{-3} \). The Decay Classes are a function of time, from the most recent wood decay stage to the oldest.


```{r cars}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

